%-------------------------
% Resume in Latex
% Author: Ojas Tyagi
% Based off of: https://github.com/sb2nov/resume & https://github.com/jakegut/resume
% License: MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{fontawesome5}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
\usepackage[sfdefault]{noto-sans}
% \usepackage[light]{sourcesanspro} % Light font weight
% \usepackage[regular]{sourcesanspro} % Regular font weight
% \usepackage[semibold]{sourcesanspro} % Semi-bold font weight
% \usepackage[bold]{sourcesanspro} % Bold font weight


% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textit{\small #2} \\
    \end{tabular*}\vspace{-4 pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\newcommand{\skillItem}[1]{\resumeItem{#1}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://megablaster.dev/}{\Large Ojas Tyagi}}\\
  \small \href{mailto:ojas@megablaster.dev}{\underline{ojas@megablaster.dev}} $|$ 
    \href{https://linkedin.com/in/ojastyagi}{\underline{linkedin.com/in/ojastyagi}} $|$
    \href{https://github.com/devmegablaster}{\underline{github.com/devmegablaster}}
    \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Vellore Institute of Technology}{Vellore, India}
      {Bachelor of Technology in Computer Engineering}{September 2021 | July 2025}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
  \resumeSubheading
      {Superjoin (Previously StackIt)}{Bengaluru, IN}
      {\textbf{Software Developer}}{ August 2023 | July 2024}
      \resumeItemListStart
        \resumeItem
        {\textbf{Optimized Data Integration with Kafka and REST APIs}: Enhanced data transfer efficiency, reducing manual efforts by 40\% and enabling seamless automation of integration workflows.}
        \resumeItem
        {\textbf{Boosted Revenue with Stripe Paywall and Secure Collaboration Features}: Implemented a frictionless paywall, increasing subscriptions by 25\%, and introduced secure connection sharing within organizations to safeguard sensitive keys.}
        \resumeItem
        {\textbf{Streamlined Deployment with CI/CD Pipelines}: Designed and implemented Jenkins pipelines, reducing deployment time by 50\% for production and pre-production environments. Added automated reporting features to deliver real-time data insights via Slack and email.}
        \resumeItem
        {\textbf{Engineered Efficient Data Previews for Imports}: Developed an optimized system to render data previews before final import, improving speed and resource utilization by 100\%, enhancing user experience and system performance.}
      \resumeItemListEnd
    \resumeSubheading
      {Onboarding.club}{Remote}
      {\textbf{Full Stack Developer}}{ December 2023 | March 2024}
      \resumeItemListStart
        \resumeItem
          {\textbf{Migrated Backend and Database}: Transitioned from Golang to TypeScript and from PostgreSQL to MongoDB, enhancing scalability and development speed while eliminating migration hassles, leading to a 30\% reduction in development time.}
        \resumeItem
          {\textbf{Innovated Platform Features and Integrated Activity Heatmaps}: Built features for gigs, blogs, rewards, and profiling, increasing user growth by 40\%. Added heatmaps for activities like blockchain and GitHub contributions, boosting user engagement by 25\%.}
        \resumeItem
          {\textbf{Orchestrated Stellar Builder House}: Led the first global Stellar Builder House, attracting builders from across the country to develop products within a week, with participants having the opportunity to secure \$100K in grants.}
      \resumeItemListEnd
      
% --------Multiple Positions Heading------------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------


  \resumeSubHeadingListEnd

%
% --------TECHINCAL SKILLS ------------

\section{Technical Skills}
\resumeSubHeadingListStart
  \skillItem{\textbf{Programming Languages}}
    {Go, C/C++, Python, JavaScript/TypeScript, Lua, R, SQL}
  \skillItem{\textbf{Libraries/ Frameworks}}
    {Echo, Gorm, Cobra, Bubbletea, Express, Jest, React, React Native, NextJS, TailwindCSS, Redux, gRPC, Protobuf}
  \skillItem{\textbf{Developer Tools \& Platforms}}
    {Git, Bash, Unix, Nix, GitHub, Docker, AWS, GCP, Firebase, MongoDB, PostgreSQL, Redis, Jenkins, Apache Kafka, Kubernetes}
\resumeSubHeadingListEnd

%-------------------------------------------


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
\resumeProjectHeading
  {\href{https://github.com/devmegablaster/jatt}{\textbf{Jatt} - \faIcon{link}}}{Go}
    \resumeSubItem
      {A lightning-fast static site generator in Go, building sites in \textbf{~5ms}. Features a simple YAML configuration and a 3-step build process for seamless, customizable, and efficient static site creation.}
  \resumeProjectHeading
    {\href{https://github.com/devmegablaster/sheetbridge}{\textbf{SheetBridge} - \faIcon{link}}}{Go, Kafka, Protobuf}
    \resumeSubItem
      {Engineered a real-time synchronization service to mirror a PostgreSQL database in Google Sheets, ensuring data consistency across both platforms. Leveraged Apache Kafka for change streams and Protocol Buffers for efficient inter-service communication.}
  \resumeProjectHeading
    {\href{https://github.com/devmegablaster/termtor}{\textbf{Termtor} - \faIcon{link}}}{Go, Bubbletea}
    \resumeSubItem
      {A lightweight and intuitive torrent client built in Go, designed for seamless command-line usage. Termtor leverages the Bubbletea framework for a modern, user-friendly interface, providing efficient torrent management with minimal resource consumption.}
  \resumeProjectHeading
    {\href{https://github.com/devmegablaster/turbokey}{\textbf{TurboKey} - \faIcon{link}}}{Go}
    \resumeSubItem
      {Built a high-performance TCP-based key-value store with 30\% faster data retrieval and support for 10,000 concurrent connections. Integrated the RESP protocol for seamless Redis compatibility, reducing migration effort by nearly 100\%.}
  \resumeSubHeadingListEnd
%-------------------------------------------

%
% --------VOLUNTEER EXPERIENCE ------------

\section{Volunteer Experience}
  \resumeSubHeadingListStart
  \resumeSubItem
      {Core Member, \href{https://www.linkedin.com/company/dscvit/}{\underline{(GDSC) Google Developer Student club}}, Vellore Institute of Technology, Vellore.  2021|2023}
    \resumeSubItem
      {Core Member \href{https://www.linkedin.com/company/codechefvit/}{\underline{Codechef}}, Vellore Institute of Technology, Vellore. 2021|2023}
    \resumeSubItem
      {Event Coordinator at \href{https://www.linkedin.com/company/gravitas-vit/}{\underline{ Gravitas 2022 }}, Vellore Institute of Technology.}
  \resumeSubHeadingListEnd
%-------------------------------------------

\end{document}
